\tool

### 2017-11-28 paper/paper.tex
1 page intro

Althouth quality is a primary concern for software producers and consumers, developers often ignore these useful tools which help improve the quality of their code~\cite{Johnson2013Why}. There are many barriers to tool adoption, and one of the main reasons useful tools are ignored or underutilized is because of the discoverability barrier. This refers to when users are unaware of tools' existence in software~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness can lead to significant amounts of wasted time and money in the software industry.

@@

To solve the static analysis tool discovery problem, we developed a new recommender system called \textit{\tool}. \tool was designed to automatically recommend static analysis tools to software engineers. We designed our system to make suggestions by integrating characteristics of peer interactions and concepts from the software engineering industry. To evaluate the effectiveness of our system, we studied the following research questions (RQs): \\

>>>>

Althouth quality is a primary concern for software producers and consumers, developers often ignore these useful tools which help improve the quality of their code~\cite{Johnson2013Why}. There are many barriers to tool adoption, and one of the main reasons useful tools are ignored or underutilized is the discoverability barrier. This refers to when users are unaware of a tool's existence within software~\cite{Murphy-HillScreencastingDiscovery}. The tool discovery problem will continue to persist as applications become more ``bloated'' with features~\cite{SoftwareBloat}. This lack of awareness of static analysis tools can lead to significant amounts of wasted time and money in the software industry.

@@

To solve the static analysis tool discovery problem, we developed a new recommender system called~\textit{\tool}. \tool~was designed to automatically recommend static analysis tools to software engineers. Previous research has shown that user-to-user recommendations, or peer interactions, are the most effective mode of increasing awareness of tools among software users~\cite{PeerInteraction}. We designed our system to make suggestions by integrating characteristics of peer interactions and concepts from the software engineering industry. To evaluate the effectiveness of our system, we studied the following research questions (RQs): \\
